Binocular integration of chromatic and luminance signals

### 2024-09-15 manuscript.qmd
Implemented further reviewer suggestions

---
title: "Binocular integration of chromatic and luminance signals"
author:
  - name: Daniel H. Baker$^{1,2,*}$
  - name: Kirralise J. Hansford$^1$
  - name: Federico G. Segala$^1$
  - name: Annie Y. Morsi$^1$
  - name: Rowan J. Huxley$^{1,3}$
  - name: Joel T. Martin$^{1,4}$
  - name: Maya Rockman$^1$
  - name: Alex R. Wade$^{1,2}$
pdf-engine: xelatex
bibliography: references.bib
csl: journal-of-vision.csl
format:
  pdf:
    keep-tex: true
#   docx
# prefer-html: true
header-includes: 
  \usepackage{lineno} \linenumbers
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
---

@@

Much progress has been made in understanding how the brain combines signals from the two eyes. However, most of this work has involved achromatic (black and white) stimuli, and it is not clear if the same processes apply in colour-sensitive pathways. In our first experiment, we measured contrast discrimination ('dipper') functions for four key ocular configurations (monocular, binocular, half-binocular and dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M) sine-wave grating stimuli. We find a similar pattern of results across stimuli, implying equivalently strong interocular suppression within each pathway. Our second experiment measured dichoptic masking within and between pathways using the method of constant stimuli. Masking was strongest within-pathway, and weakest between S-(L+M) and achromatic mechanisms. Finally, we repeated the dipper experiment using temporal luminance modulations, which produced slightly weaker interocular suppression than for spatially modulated stimuli. We interpret our results in the context of a contemporary two-stage model of binocular contrast gain control, implemented here using a hierarchical Bayesian framework. Posterior distributions of the weight of interocular suppression overlapped with a value of 1 for all dipper data sets, and the model captured well the pattern of thresholds from all three experiments.

@@

At the output of the human retina, cone responses are split into three distinct pathways. The sum of long- and medium-wavelength cone outputs (L+M) transmits luminance information [see @Sharpe2011], and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above). The difference of long- and medium-wavelength cone outputs (L-M) is responsive to chromatic stimuli modulating along a red/green axis in colour space. Finally the opponent (S-(L+M)) channel codes chromatic stimuli modulating along a blue/yellow axis. At isoluminance, where (L+M) is held constant, this channel is driven purely by the S-cone outputs. Within each chromatic pathway, contrast discrimination functions are similar to those for achromatic vision, showing evidence of facilitation at low pedestal contrasts and masking at high pedestal contrasts [@Switkes1988; @Chen2000]. There are also interactions between luminance and colour mechanisms, which are able to mask each other [@Switkes1988; @Mullen1994; @Chen2000], and under some circumstances also show cross-pathway facilitation [@Switkes1988; @Cole1990; @Mullen1994; @Shooner2020].

There has not yet been a detailed investigation of binocular contrast interactions in either chromatic pathway, however there are reasons to believe they may differ from the achromatic pathway. At detection threshold, binocular summation is greater for chromatic versus achromatic stimuli [@Simmons2005], implying a more linear initial stage of processing. For cross-orientation masking, there are differences in the magnitude of masking between chromatic (L-M) and achromatic stimuli [@Kim2013; @Medina2009], as well as differences in their temporal dynamics [@Kim2015]. There are also binocular interactions between chromatic and achromatic pathways [@Mullen2014; @Kingdom2015], yet these have not been fully explored for arrangements where the target and mask have the same orientation. Finally, the neurophysiological underpinnings of colour vision may be distinct from those of the achromatic system. The classical view is that in primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981], and are largely monocular [@Livingstone1984]. However subsequent work has revealed a more complex arrangement, making such a clear-cut phyisological distinction unlikely [for a review, see @Shapley2011]. Nevertheless, the physiological segregation between pathways at the output of the retina could still lead to differences in the way signals are combined across the eyes.

@@

We additionally implemented a hierarchical Bayesian version of the model to estimate full posterior parameter distributions. This model was fit simultaneously to the full trial-by-trial data from all participants who participated in a given experiment (i.e. the model was fitted separately to each of the four dipper data sets). [@fig-bayesianmodel]a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically. Modal posterior parameter values (maximum a posteriori (MAP) estimates) are given in the lower rows of @tbl-parametertable. These are in a similar range to the parameters from the simplex fitting and the original @Meese2006 parameters (reproduced in the first row of the table for reference). The panels along the right and upper margins of [@fig-bayesianmodel] show posterior distributions for each model parameter. Note in particular that the posterior distribution for the weight of interocular suppression ($\omega$, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data. We note that the distribution for $\omega$ in the flickering disc condition is somewhat lower than for the other three data sets. However this difference is not meaningful according to widely accepted criteria such as comparing the 95% intervals of the distribution to a value of $\omega=1$.

@@

In V1, the classical view is that chromatic stimuli are processed in 'blob' regions that are largely monocular as they fall within ocular dominance columns [@Livingstone1984]. However more recent work has shown chromatic processing outside of the blobs [@Sincich2005], especially for stimuli with spatial structure [@Chatterjee2021]. Since our psychophysical results indicate that interocular suppression is equally strong within chromatic and achromatic pathways, it may be that psychophysical performance indexes a common population of (non-blob) neurons for all of our stimuli. On the other hand, if blob regions include a subset of monocular neurons subject to interocular suppression [e.g. @Dougherty2019], this might be followed by binocular summation at a later stage of processing for chromatic stimuli, and potentially also for very low spatial frequency luminance modulations also processed in blobs [@Economides2011].

>>>>

---
title: "Binocular integration of chromatic and luminance signals"
author:
  - name: Daniel H. Baker$^{1,2,*}$
  - name: Kirralise J. Hansford$^1$
  - name: Federico G. Segala$^1$
  - name: Anisa Y. Morsi$^1$
  - name: Rowan J. Huxley$^{1,3}$
  - name: Joel T. Martin$^{1,4}$
  - name: Maya Rockman$^1$
  - name: Alex R. Wade$^{1,2}$
pdf-engine: xelatex
bibliography: references.bib
csl: journal-of-vision.csl
# prefer-html: true
format:
    pdf:
      keep-tex: true
  # docx
header-includes: 
  \usepackage{lineno} \linenumbers
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
---

@@

Much progress has been made in understanding how the brain combines signals from the two eyes. However, most of this work has involved achromatic (black and white) stimuli, and it is not clear if the same processes apply in colour-sensitive pathways. In our first experiment, we measured contrast discrimination ('dipper') functions for four key ocular configurations (monocular, binocular, half-binocular and dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M) sine-wave grating stimuli (L: long-, M: medium-, S: short-wavelength). We find a similar pattern of results across stimuli, implying equivalently strong interocular suppression within each pathway. Our second experiment measured dichoptic masking within and between pathways using the method of constant stimuli. Masking was strongest within-pathway, and weakest between S-(L+M) and achromatic mechanisms. Finally, we repeated the dipper experiment using temporal luminance modulations, which produced slightly weaker interocular suppression than for spatially modulated stimuli. We interpret our results in the context of a contemporary two-stage model of binocular contrast gain control, implemented here using a hierarchical Bayesian framework. Posterior distributions of the weight of interocular suppression overlapped with a value of 1 for all dipper data sets, and the model captured well the pattern of thresholds from all three experiments.

@@

At the output of the human retina, cone responses are split into three distinct pathways. The sum of long- (L) and medium- (M) wavelength cone outputs (L+M) transmits luminance information [see @Sharpe2011], and is likely responsible for the binocular combination effects previously studied using achromatic stimuli (see above). The difference of long- and medium-wavelength cone outputs (L-M) is responsive to chromatic stimuli modulating along a red/green axis in colour space. Finally the opponent short-wavelength (S) channel codes chromatic stimuli modulating along a blue/yellow axis (S-(L+M)). At isoluminance, where (L+M) is held constant, this channel is driven purely by the S-cone outputs. Note that we use these shorthand terms throughout to refer to chromatic mechanisms, but acknowledge that in reality the photoreceptor outputs are weighted, for example S-0.5(L+M), and 3L+M. Within each chromatic pathway, contrast discrimination functions (which plot discrimination thresholds against pedestal contrast; sometimes referred to as TvC functions) are similar to those for achromatic vision, showing evidence of facilitation at low pedestal contrasts and masking at high pedestal contrasts [@Switkes1988; @Chen2000]. There are also interactions between luminance and colour mechanisms, which are able to mask each other [@Switkes1988; @Mullen1994; @Chen2000], and under some circumstances also show cross-pathway facilitation [@Switkes1988; @Cole1990; @Mullen1994; @Shooner2020].

There has not yet been a detailed investigation of binocular contrast interactions in either chromatic pathway, however there are reasons to believe they may differ from the achromatic pathway. At detection threshold, binocular summation is greater for chromatic versus achromatic stimuli [@Simmons2005], implying a more linear initial stage of processing. For cross-orientation masking, there are differences in the magnitude of masking between chromatic (L-M) and achromatic stimuli [@Kim2013; @Medina2009], as well as differences in their temporal dynamics [@Kim2015]. There are also binocular interactions between chromatic and achromatic pathways [@Mullen2014; @Kingdom2015], yet these have not been fully explored for arrangements where the target and mask have the same orientation. Finally, the neurophysiological underpinnings of colour vision may be distinct from those of the achromatic system. The classical view was that in primary visual cortex (V1), chromatic signals are processed in 'blob' regions that are revealed by cytochrome oxidase staining [@Horton1981], and are largely monocular [@Livingstone1984]. However subsequent work has revealed a large population of colour-luminance neurons with a subset of colour-only ones, making such a clear-cut physiological distinction unlikely [for a review, see @Shapley2011]. Nevertheless, the physiological segregation between pathways at the output of the retina could still lead to differences in the way signals are combined across the eyes.

@@

We additionally implemented a hierarchical Bayesian version of the model to estimate full posterior parameter distributions. This model was fit simultaneously to the full trial-by-trial data from all participants who completed a given experiment (i.e. the model was fitted separately to each of the four dipper data sets). [@fig-bayesianmodel]a-d summarises the model behaviour, which displays the same pattern of dipper functions as we found empirically. Modal posterior parameter values (maximum a posteriori (MAP) estimates) are given in the lower rows of @tbl-parametertable. These are in a similar range to the parameters from the simplex fitting and the original @Meese2006 parameters (reproduced in the first row of the table for reference). The panels along the right and upper margins of [@fig-bayesianmodel] show posterior distributions for each model parameter. Note in particular that the posterior distribution for the weight of interocular suppression ($\omega$, top right panel) overlaps 1 for each experiment, consistent with the strong dichoptic masking observed in the threshold data. We note that the distribution for $\omega$ in the flickering disc condition is somewhat lower than for the other three data sets. However this difference is not meaningful according to widely accepted criteria such as comparing the 95% intervals of the distribution to a value of $\omega=1$.

@@

In V1, the classical view was that chromatic stimuli are processed in 'blob' regions that are largely monocular as they fall within ocular dominance columns [@Livingstone1984]. However more recent work has shown chromatic processing outside of the blobs [@Sincich2005], especially for stimuli with spatial structure [@Chatterjee2021]. Since our psychophysical results indicate that interocular suppression is equally strong within chromatic and achromatic pathways, it may be that psychophysical performance indexes a common population of (non-blob) neurons for all of our stimuli. On the other hand, if blob regions include a subset of monocular neurons subject to interocular suppression [e.g. @Dougherty2019], this might be followed by binocular summation at a later stage of processing for chromatic stimuli, and potentially also for very low spatial frequency luminance modulations also processed in blobs [@Economides2011].

### 2024-09-15 manuscript.tex
Implemented further reviewer suggestions

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Binocular integration of chromatic and luminance signals},
  pdfauthor={Daniel H. Baker\^{}\{1,2,*\}; Kirralise J. Hansford\^{}1; Federico G. Segala\^{}1; Annie Y. Morsi\^{}1; Rowan J. Huxley\^{}\{1,3\}; Joel T. Martin\^{}\{1,4\}; Maya Rockman\^{}1; Alex R. Wade\^{}\{1,2\}},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Binocular integration of chromatic and luminance signals}
\author{Daniel H. Baker\(^{1,2,*}\) \and Kirralise J.
Hansford\(^1\) \and Federico G. Segala\(^1\) \and Annie Y.
Morsi\(^1\) \and Rowan J. Huxley\(^{1,3}\) \and Joel T.
Martin\(^{1,4}\) \and Maya Rockman\(^1\) \and Alex R. Wade\(^{1,2}\)}
\date{}

@@

Much progress has been made in understanding how the brain combines
signals from the two eyes. However, most of this work has involved
achromatic (black and white) stimuli, and it is not clear if the same
processes apply in colour-sensitive pathways. In our first experiment,
we measured contrast discrimination (`dipper') functions for four key
ocular configurations (monocular, binocular, half-binocular and
dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M)
sine-wave grating stimuli. We find a similar pattern of results across
stimuli, implying equivalently strong interocular suppression within
each pathway. Our second experiment measured dichoptic masking within
and between pathways using the method of constant stimuli. Masking was
strongest within-pathway, and weakest between S-(L+M) and achromatic
mechanisms. Finally, we repeated the dipper experiment using temporal
luminance modulations, which produced slightly weaker interocular
suppression than for spatially modulated stimuli. We interpret our
results in the context of a contemporary two-stage model of binocular
contrast gain control, implemented here using a hierarchical Bayesian
framework. Posterior distributions of the weight of interocular
suppression overlapped with a value of 1 for all dipper data sets, and
the model captured well the pattern of thresholds from all three
experiments.

@@

At the output of the human retina, cone responses are split into three
distinct pathways. The sum of long- and medium-wavelength cone outputs
(L+M) transmits luminance information (see Sharpe et al., 2011), and is
likely responsible for the binocular combination effects previously
studied using achromatic stimuli (see above). The difference of long-
and medium-wavelength cone outputs (L-M) is responsive to chromatic
stimuli modulating along a red/green axis in colour space. Finally the
opponent (S-(L+M)) channel codes chromatic stimuli modulating along a
blue/yellow axis. At isoluminance, where (L+M) is held constant, this
channel is driven purely by the S-cone outputs. Within each chromatic
pathway, contrast discrimination functions are similar to those for
achromatic vision, showing evidence of facilitation at low pedestal
contrasts and masking at high pedestal contrasts (Chen et al., 2000;
Switkes et al., 1988). There are also interactions between luminance and
colour mechanisms, which are able to mask each other (Chen et al., 2000;
Mullen \& Losada, 1994; Switkes et al., 1988), and under some
circumstances also show cross-pathway facilitation (Cole et al., 1990;
Mullen \& Losada, 1994; Shooner \& Mullen, 2020; Switkes et al., 1988).

There has not yet been a detailed investigation of binocular contrast
interactions in either chromatic pathway, however there are reasons to
believe they may differ from the achromatic pathway. At detection
threshold, binocular summation is greater for chromatic versus
achromatic stimuli (Simmons, 2005), implying a more linear initial stage
of processing. For cross-orientation masking, there are differences in
the magnitude of masking between chromatic (L-M) and achromatic stimuli
(Kim et al., 2013; Medina \& Mullen, 2009), as well as differences in
their temporal dynamics (Kim \& Mullen, 2015). There are also binocular
interactions between chromatic and achromatic pathways (Kingdom \&
Libenson, 2015; Mullen et al., 2014), yet these have not been fully
explored for arrangements where the target and mask have the same
orientation. Finally, the neurophysiological underpinnings of colour
vision may be distinct from those of the achromatic system. The
classical view is that in primary visual cortex (V1), chromatic signals
are processed in `blob' regions that are revealed by cytochrome oxidase
staining (Horton \& Hubel, 1981), and are largely monocular (Livingstone
\& Hubel, 1984). However subsequent work has revealed a more complex
arrangement, making such a clear-cut phyisological distinction unlikely
(for a review, see Shapley \& Hawken, 2011). Nevertheless, the
physiological segregation between pathways at the output of the retina
could still lead to differences in the way signals are combined across
the eyes.

@@

We additionally implemented a hierarchical Bayesian version of the model
to estimate full posterior parameter distributions. This model was fit
simultaneously to the full trial-by-trial data from all participants who
participated in a given experiment (i.e.~the model was fitted separately
to each of the four dipper data sets). Figure~\ref{fig-bayesianmodel}a-d
summarises the model behaviour, which displays the same pattern of
dipper functions as we found empirically. Modal posterior parameter
values (maximum a posteriori (MAP) estimates) are given in the lower
rows of Table~\ref{tbl-parametertable}. These are in a similar range to
the parameters from the simplex fitting and the original Meese et al.
(2006) parameters (reproduced in the first row of the table for
reference). The panels along the right and upper margins of
Figure~\ref{fig-bayesianmodel} show posterior distributions for each
model parameter. Note in particular that the posterior distribution for
the weight of interocular suppression (\(\omega\), top right panel)
overlaps 1 for each experiment, consistent with the strong dichoptic
masking observed in the threshold data. We note that the distribution
for \(\omega\) in the flickering disc condition is somewhat lower than
for the other three data sets. However this difference is not meaningful
according to widely accepted criteria such as comparing the 95\%
intervals of the distribution to a value of \(\omega=1\).

@@

In V1, the classical view is that chromatic stimuli are processed in
`blob' regions that are largely monocular as they fall within ocular
dominance columns (Livingstone \& Hubel, 1984). However more recent work
has shown chromatic processing outside of the blobs (Sincich \& Horton,
2005), especially for stimuli with spatial structure (Chatterjee et al.,
2021). Since our psychophysical results indicate that interocular
suppression is equally strong within chromatic and achromatic pathways,
it may be that psychophysical performance indexes a common population of
(non-blob) neurons for all of our stimuli. On the other hand, if blob
regions include a subset of monocular neurons subject to interocular
suppression (e.g. Dougherty et al., 2019), this might be followed by
binocular summation at a later stage of processing for chromatic
stimuli, and potentially also for very low spatial frequency luminance
modulations also processed in blobs (Economides et al., 2011).

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Binocular integration of chromatic and luminance signals},
  pdfauthor={Daniel H. Baker\^{}\{1,2,*\}; Kirralise J. Hansford\^{}1; Federico G. Segala\^{}1; Anisa Y. Morsi\^{}1; Rowan J. Huxley\^{}\{1,3\}; Joel T. Martin\^{}\{1,4\}; Maya Rockman\^{}1; Alex R. Wade\^{}\{1,2\}},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Binocular integration of chromatic and luminance signals}
\author{Daniel H. Baker\(^{1,2,*}\) \and Kirralise J.
Hansford\(^1\) \and Federico G. Segala\(^1\) \and Anisa Y.
Morsi\(^1\) \and Rowan J. Huxley\(^{1,3}\) \and Joel T.
Martin\(^{1,4}\) \and Maya Rockman\(^1\) \and Alex R. Wade\(^{1,2}\)}
\date{}

@@

Much progress has been made in understanding how the brain combines
signals from the two eyes. However, most of this work has involved
achromatic (black and white) stimuli, and it is not clear if the same
processes apply in colour-sensitive pathways. In our first experiment,
we measured contrast discrimination (`dipper') functions for four key
ocular configurations (monocular, binocular, half-binocular and
dichoptic), for achromatic, isoluminant L-M and isoluminant S-(L+M)
sine-wave grating stimuli (L: long-, M: medium-, S: short-wavelength).
We find a similar pattern of results across stimuli, implying
equivalently strong interocular suppression within each pathway. Our
second experiment measured dichoptic masking within and between pathways
using the method of constant stimuli. Masking was strongest
within-pathway, and weakest between S-(L+M) and achromatic mechanisms.
Finally, we repeated the dipper experiment using temporal luminance
modulations, which produced slightly weaker interocular suppression than
for spatially modulated stimuli. We interpret our results in the context
of a contemporary two-stage model of binocular contrast gain control,
implemented here using a hierarchical Bayesian framework. Posterior
distributions of the weight of interocular suppression overlapped with a
value of 1 for all dipper data sets, and the model captured well the
pattern of thresholds from all three experiments.

@@

At the output of the human retina, cone responses are split into three
distinct pathways. The sum of long- (L) and medium- (M) wavelength cone
outputs (L+M) transmits luminance information (see Sharpe et al., 2011),
and is likely responsible for the binocular combination effects
previously studied using achromatic stimuli (see above). The difference
of long- and medium-wavelength cone outputs (L-M) is responsive to
chromatic stimuli modulating along a red/green axis in colour space.
Finally the opponent short-wavelength (S) channel codes chromatic
stimuli modulating along a blue/yellow axis (S-(L+M)). At isoluminance,
where (L+M) is held constant, this channel is driven purely by the
S-cone outputs. Note that we use these shorthand terms throughout to
refer to chromatic mechanisms, but acknowledge that in reality the
photoreceptor outputs are weighted, for example S-0.5(L+M), and 3L+M.
Within each chromatic pathway, contrast discrimination functions (which
plot discrimination thresholds against pedestal contrast; sometimes
referred to as TvC functions) are similar to those for achromatic
vision, showing evidence of facilitation at low pedestal contrasts and
masking at high pedestal contrasts (Chen et al., 2000; Switkes et al.,
1988). There are also interactions between luminance and colour
mechanisms, which are able to mask each other (Chen et al., 2000; Mullen
\& Losada, 1994; Switkes et al., 1988), and under some circumstances
also show cross-pathway facilitation (Cole et al., 1990; Mullen \&
Losada, 1994; Shooner \& Mullen, 2020; Switkes et al., 1988).

There has not yet been a detailed investigation of binocular contrast
interactions in either chromatic pathway, however there are reasons to
believe they may differ from the achromatic pathway. At detection
threshold, binocular summation is greater for chromatic versus
achromatic stimuli (Simmons, 2005), implying a more linear initial stage
of processing. For cross-orientation masking, there are differences in
the magnitude of masking between chromatic (L-M) and achromatic stimuli
(Kim et al., 2013; Medina \& Mullen, 2009), as well as differences in
their temporal dynamics (Kim \& Mullen, 2015). There are also binocular
interactions between chromatic and achromatic pathways (Kingdom \&
Libenson, 2015; Mullen et al., 2014), yet these have not been fully
explored for arrangements where the target and mask have the same
orientation. Finally, the neurophysiological underpinnings of colour
vision may be distinct from those of the achromatic system. The
classical view was that in primary visual cortex (V1), chromatic signals
are processed in `blob' regions that are revealed by cytochrome oxidase
staining (Horton \& Hubel, 1981), and are largely monocular (Livingstone
\& Hubel, 1984). However subsequent work has revealed a large population
of colour-luminance neurons with a subset of colour-only ones, making
such a clear-cut physiological distinction unlikely (for a review, see
Shapley \& Hawken, 2011). Nevertheless, the physiological segregation
between pathways at the output of the retina could still lead to
differences in the way signals are combined across the eyes.

@@

We additionally implemented a hierarchical Bayesian version of the model
to estimate full posterior parameter distributions. This model was fit
simultaneously to the full trial-by-trial data from all participants who
completed a given experiment (i.e.~the model was fitted separately to
each of the four dipper data sets). Figure~\ref{fig-bayesianmodel}a-d
summarises the model behaviour, which displays the same pattern of
dipper functions as we found empirically. Modal posterior parameter
values (maximum a posteriori (MAP) estimates) are given in the lower
rows of Table~\ref{tbl-parametertable}. These are in a similar range to
the parameters from the simplex fitting and the original Meese et al.
(2006) parameters (reproduced in the first row of the table for
reference). The panels along the right and upper margins of
Figure~\ref{fig-bayesianmodel} show posterior distributions for each
model parameter. Note in particular that the posterior distribution for
the weight of interocular suppression (\(\omega\), top right panel)
overlaps 1 for each experiment, consistent with the strong dichoptic
masking observed in the threshold data. We note that the distribution
for \(\omega\) in the flickering disc condition is somewhat lower than
for the other three data sets. However this difference is not meaningful
according to widely accepted criteria such as comparing the 95\%
intervals of the distribution to a value of \(\omega=1\).

@@

In V1, the classical view was that chromatic stimuli are processed in
`blob' regions that are largely monocular as they fall within ocular
dominance columns (Livingstone \& Hubel, 1984). However more recent work
has shown chromatic processing outside of the blobs (Sincich \& Horton,
2005), especially for stimuli with spatial structure (Chatterjee et al.,
2021). Since our psychophysical results indicate that interocular
suppression is equally strong within chromatic and achromatic pathways,
it may be that psychophysical performance indexes a common population of
(non-blob) neurons for all of our stimuli. On the other hand, if blob
regions include a subset of monocular neurons subject to interocular
suppression (e.g. Dougherty et al., 2019), this might be followed by
binocular summation at a later stage of processing for chromatic
stimuli, and potentially also for very low spatial frequency luminance
modulations also processed in blobs (Economides et al., 2011).
